### 2020-01-29 paper/sex_selection_spacing-ver3.tex
Minor edits in paper

Understanding the changes in birth spacing is essential for three reasons.

First, tempo effects, arising from changes in birth spacing, bias the total 
fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
If birth spacing increased substantially over time, India's fertility may, in 
fact, be substantially higher than what is generally accepted based on the TFR.

@@

Finally, birth spacing has long served as a measure of son preference, with strong
son preference associated with shorter birth intervals, the fewer sons a family has 
\citep{ben-porath76b,Leung1988}.
Now, longer birth intervals in the absence of sons, rather than an indicator of 
lower son preference, may instead arise because couples with a strong preference 
for sons use sex selection, possibly to the point where we observe a reversal of 
the traditional spacing pattern.
Despite a large literature on son preference and birth spacing, there is, however,
no prior research has examined how sex selection affects spacing.

@@

[TK things to cover:
- almost everybody marry, so these numbers should reflect cohort fertility relatively well
- what happens when women begin to join the labor force in larger numbers?
- better job oppportunities may be a direct way to affect sex selection since it makes 
it more expensive to have long spacing
]

>>>>

Understanding how birth spacing changes is essential for three reasons.

First, tempo effects, here arising from changes in birth spacing, bias 
the total fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
If birth spacing increased substantially over time, India's fertility may, in 
fact, be higher than what is generally accepted based on the TFR.

@@

Finally, birth spacing has long served as a measure of son preference, with strong
son preference associated with shorter birth intervals, the fewer sons a family has 
\citep{ben-porath76b,Leung1988}.
Now, longer birth intervals in the absence of sons, rather than an indicator of 
lower son preference, may instead arise because couples with a strong preference 
for sons use sex selection, possibly to the point where we observe a reversal of 
the traditional spacing pattern.
Despite a large literature on son preference and birth spacing, there is, however,
no prior research that has examined how sex selection affects spacing.

@@

[TK things to cover:
- almost everybody marry, so these numbers should reflect cohort fertility relatively well
- what happens when women begin to join the labor force in larger numbers?
- better job oppportunities may be a direct way to affect sex selection since it makes 
it more expensive to have long spacing
- Incorporate Newman 1984 discussion (p 947) on income vs substitution effect
- why has fertility fallen at all? Lower mortality, higher quality children?
]
